\textbf{EECS 340: Assignment 1}

### 2020-01-28 assignment_1/article.tex
💄 Polish language based on Grammly.

Assume we had $x, y$ in the pervious iteration, for this iteration we shall have $x', y'$. Without loss of generality, assume $x > y$, we must have the following according to the algorithm:
\begin{gather}
    x' = x - y \nonumber\\
    y' = x \nonumber
\end{gather}

@@

As there is no $(a, b)$ combination available to form $a+b = x$, we must increse the value of index $i$ in the case of $k < x$ to achieve a hopefully greather $k'$ in the next interation; and similarly, to decrese the value of index $j$ to achieve a hopefully lesser $k'$ in the case of $k > x$. Thus, the conditional statements in the pseudocode in \textbf{Section 2.1} are justified, and the algorithm is proven to be correct.

\subsection{(d)}
The worst case of this algorithm is when it returns \inlinecode{False}. In such case we will have $i$ and $j$ traveling the entire bound of $\mathbb{Z^+} \in [0, n)$. The loop will execute $2n$ times, thus the run time is $\Theta(n)$.

@@

Thus, we may infer that if $n$ is odd, a \textit{Pisidian} shall remain. Otherwise if $n$ is even, a \textit{Lydian} shall remain.

>>>>

Assume we had $x, y$ in the previous iteration, for this iteration we shall have $x', y'$. Without loss of generality, assume $x > y$, we must have the following according to the algorithm:
\begin{gather}
    x' = x - y \nonumber\\
    y' = x \nonumber
\end{gather}

@@

As there is no $(a, b)$ combination available to form $a+b = x$, we must increase the value of index $i$ in the case of $k < x$ to achieve a hopefully greater $k'$ in the next iteration; and similarly, to decrease the value of index $j$ to achieve a hopefully lesser $k'$ in the case of $k > x$. Thus, the conditional statements in the pseudocode in \textbf{Section 2.1} are justified, and the algorithm is proven to be correct.

\subsection{(d)}
The worst case of this algorithm is when it returns \inlinecode{False}. In such case, we will have $i$ and $j$ traveling the entire bound of $\mathbb{Z^+} \in [0, n)$. The loop will execute $2n$ times; thus the run time is $\Theta(n)$.

@@

Thus, we may infer that if $n$ is odd, a \textit{Pisidian} shall remain. Otherwise, if $n$ is even, a \textit{Lydian} shall remain.
